### 2016-07-15 version0.0/paper3.tex
finishing intro0.0
Adding summary

\chapter{Data Mining in Nearby Galaxies}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} %%( I am not really happy with this introduction but it is the best I can have for now:/ )
%General information about galaxies %(Maybe it is too generic?!!)
Inside each galaxy, there are millions of stars and large amount of dust and gas, which all affect on each others' formation, evolution and extinction.
Galaxies are an active and complicated systems, that are constantly changing.
There are extensive amount of studies about correlations between galaxies' emission and their physical properties, both observationally and theoretically %(Some references here). 
These studies expands our knowledge of the underlying processes in formation and evolution of galaxies every day, but the details of how these process work are still undetermined.

% Nearby galaxies and their importance 
Nearby galaxies play an important role in learning about galaxies' formation and evolution.
These galaxies are close enough to be able to observe various regions inside them in details.
As a result, many studies are devoted to find relations between physical properties of the galaxies in both spatially resolved regions and galaxies as a whole%(Some more references here)
, and many others use these results in analyzing data from high-redshift galaxies. %(Some more references here)
The amount of data that is acquired from nearby galaxies is increasing daily.
Advances in technology helps to both observe and store enormous amount of data from sky.%The sky?! 
Telescopes and surveys gather data from nearby galaxies in variuse wavelengths and from these data we can measure physical properties of galaxies (e.g. stellar mass, star formation rate (SFR), dust mass, gas mass)~\citep[e.g.][]{Calzetti07,Dale09,Eskew12}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), with a distance of $\sim$0.78~Mpc~\citep{McConnachie05}, is the closest spiral galaxy to the Milky Way.
Images of this galaxy provide us a detail view of inside of a spiral galaxy from distance.
M31 data was a target of many telescopes (e.g. {\it Hubble} \citep{Dalcanton12}, \Spitzer\citep{Wener04}, \Herschel\citep{Pilbratt10} space telescopes) and was a subject of many more studies \citep[e.g.][and references therein]{Barmby06, Gordon06, Azimlu11, Sanders12, Dim15, Rahmani16}.

\cite{Barmby06} used data from Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show evidence of Polycyclic Aromatic Hydrocarbons (PAH)s in interstellar medium (ISM) of M31.
Using the mid-IR data from Multiband Imaging Photometer for Spitzer (MIPS), \cite{Gordon06} studied the morphology of the dust in M31.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied H {\sc II} regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by~\cite{Tamm12} and~\cite{Massey07}. %%%And some from PHAT survey
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the SFR in M31 in order to study star formation laws, and \cite{Dim15} and \cite{Kapala15} used spectroscopic data of the galaxy to study PAHs and other line emissions in the ISM.

Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of undergoing processes in the galaxy.
The amount of the observed data and measured quantities of M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
Knowledge discovery and data mining methods are designed to extract hidden information from data and are tested in many astronomical studies.
However, to the best of our knowledge, this study is the first study that uses a data mining method on data from nearby galaxies. %%% ehh

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} wrote an extensive review of data mining and machine learning, and their usages in astronomy.
A data mining algorithm learns about data from sets of trainings, which can be supervised or unsupervised.
The supervised trainings refer to methods, that use examples of the desired output to learn about input data and are valuable tools to classify data with known target values.
On the contrary, the unsupervised methods train without any prior knowledge of output results. 
They solely work based on the underlying structure of input data.   
The unsupervised methods are very useful tools in knowledge discovery studies on input data, which we do not have any insight of them (or when we want to make sure that we did not miss any valuable information in our previous studies). %%% ehh to after or part.

%SOM
One the most tested methods of data mining in astronomy is the artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein12, Hossein14,Hossein16,Ellison16a}.
ANNs are designed to work in the same way that the neurons work in a human mind.
They are networks of interconnected neurons (nodes), which all of the connections are weighted.
These networks are used to study about nonlinear and complex relations between input and output data.
%These relations can be applied to the new sets of data with similar feature

One of the most well-known unsupervised neural network in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs map and visualize a complex and nonlinear high dimension data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since 1990s, many studies utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray bursts clustering and classification of light curves), and photometric redshift estimations~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b} %%% Why I cannot add submitted in front of the high-z paper

% other Unsupervised methods
The purpose of this project is to have a new insight into nearby galaxies using M31 data with focusing on relations between PAHs and other properties of the galaxy.
To fulfill this purpose, an unsupervised data mining method is the most suitable choice. %%eh  
K-means algorithm, SOMs, and hierarchical clustering are main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more

For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into desired number of the clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups, and the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing SOMs, K-means and hierarchical clustering shows that in some cases hierarchical clustering method miss-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose SOM method over K-means due to the fact that SOMs not only clusters data, but also shows similarity and dissimilarity between each cluster.
Therefore, we can cluster our sample data and study the underlying structure of data, simultaneously.

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply SOM algorithm on M31 data, and trained 1D and 2D networks.
Using smaller size networks we study the properties of the clusters and investigate relations between PAHs features with other features in M31.
We create 2D SOMs from subsets of data as well as all available data, which helps us to understand the effect of each input in the position of the clusters in the SOM, which leads to prediction of the unmeasured quantities in a galaxy.
Assuming that all the spiral nearby galaxies have similar properties, we apply 2D trained networks on data from the Pinwheel Galaxy (M101), which is another spiral nearby galaxy. 
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

In Section $\S$~\ref{Sec: data_SOMN}, we present the sample data from M31 and M101, that we use in this study. 
We describe the SOM method in Section $\S$~\ref{sec: method}. 
The results of the 1D SOM networks and studying PAHs in M31 is presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the result of 2D SOM networks and how we use them to extract information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

@@

\section{Sample of study}
\label{Sec: data_SOMN}

We gathered data from 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}) as inputs for SOMs.
We chose those specific regions due to availability of the PAHs data for them.
Besides PAHs data, for each galaxy, we chose spectroscopy and photometry data as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of the data and their unit for both M31 and M101.
We divided each values by the area of their region (in arcsec$^2$), to remove the distance factor from the data compare values of quantities in both galaxies.
Since the resolution of the data varies from less than 1$\arcsec$ to $60\arcsec \times 90 \arcsec$, any attempt to match the resolutions causes loosing all the information in some of the input data (e.g. the spectroscopic data).
On the other hand, in this project we used flux (or value of the quantities) per area as inputs of SOMs, which the convolution methods conserve it~\citep{Aniano12}.
Therefore, we did not perform any resolution matching in this paper and used data in their original resolutions.

@@

  \begin{figure*}
    \subfloat[MIPS 24~$\mu$m image of M31 from~\cite{Gordon06}, with position of 10 regions \label{fig: regions in m31}]{
      \includegraphics[width=\textwidth]{../image_paper3/images0.0/M31/M31.png}
    }
    \hfill
    \subfloat[IRAC 3.6~$\mu$m image of M101~\cite{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
      \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}}
    \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
    \label{fig:dummy}
  \end{figure*}

%M31 data 
%%%%% Sahar: More detail, right?
    \subsection{M31 data}
     \label{Sec: data_M31_SOMN}

     The 10 regions in M31 were chosen due to availability of the PAH data for them. 
     \cite{Dim15} studied PAH for those regions using {\it Spitzer}/Infrared Spectrograph~\citep[IRS,][]{Houck04b} observations. 
     They used {\sc PAHFIT IDL} tool~\citep{Smith07b} and measured fluxes and equivalent widths of PAH features as well as atomic line features.
     %For spectroscopy part of our sample, we utilized their measured fluxes for PAH lines. 
     \cite{Dim15} also measured metallicity and of radiation hardness index (RHI) for these 10 regions.
     We used the measured fluxes for PAHs featured, metallicity and RHI of each region as an input for SOMs.

     We used \GALEX FUV and NUV channels~\citep{Martin05}, \halpha, [\sii] narrow badn and [\oiii] narrow band~\citep{Massey07}, IRAC channels 1 to 4~\citep{Barmby06}, MIPS24 and 70~$\mu$m~\citep{Gordon06}, PACS100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m~\citep{Fritz12} emission for photometry part of the sample.
     We changed units of all fluxes to Wm$^{-2}$ to be the same unit as PAHs fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line~\citep{Nieten06} and the atomic gas (H\,{\sc I}) 21~cm emission from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m), stellar mass, mass of molecular clouds, mass of atomic gas (H\,{\sc I}), total gas mass, and total infrared (TIR) luminosity (L$_{\rm TIR}$) data from \cite{Rahmani16}, and L$_{\rm dust}$ and mass data from \cite{Draine14}.

    \subsection{M101 data}
    \label{Sec: data_M101_SOMN} 
     For M101 galaxy, we used PAH fluxes which had been measured using {\sc PAHFIT IDL} tool and reported in \cite{Gordon08}.
     We also added their measurement of metallicity and RHI for these regions to our sample.
     We used data available on NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather our photometry data of M101. 
     We chose data from \GALEX FUV and NUV channels~\citep{depaz07}, IRAC channels 1 to 4, MIPS~24 and 70~$\mu$m~\cite{Dale09}, and  PACS~100 and 160~$\mu$m and SPIRE250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     The Same as M31 data, we used $^{12}$CO (J:$1\rightarrow0$) line~\citep{Helfer03} and the atomic gas (H\,{\sc I}) 21~cm emission from \cite{Walter08} data.
     SFR(FUV + 24$\mu$m), stellar and total gas mass map were calculated using the same methods that M31 data were derived in \cite{Rahmani16}.

      Some of the correlations between some wavelengths and properties of galaxies are well-known.
     For example, \citep{Rahmani16} used IRAC1 band emission to calculate the stellar mass, or FUV, NUV and MIPS24 emission to measure the SFR values. 
     To make sure that we wouldn't use some of the observed data as an input data in various forms, we removed all the observed data, that were used to calculate these properties from the input sample.
     We used these sample as the main input for creating SOMs.
     Fig.~\ref{fig: cor_all} shows Pearson correlation coefficients with a confidence level of $95\%$ for the input data.

      \begin{figure}
                \centering
                \includegraphics[width=\textwidth]{../image_paper3/images0.01/cor_plots/M31_all_derived_ones_core_plot_for_paper.pdf}
            \caption{Pearson correlation coefficients with a confidence level of 95$\%$ for all the in the subset 0. The colours show the Pearson correlation coefficients where 1 means highly correlated and -1 is highly anti-correlated quantities. The non-significant correlations were left empty.}
            \label{fig: cor_all}
        \end{figure}

>>>>

\chapter{Data Mining in Nearby Galaxies}
\label{ch: paper3}
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%Intro
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Introduction} 
% Nearby galaxies and their importance 
Nearby galaxies play an important role in our understanding of galaxies' formation and evolution.
Nearby galaxies are defined as those close enough that we are able to observe their structure and composition in detail.
As a result, many studies have been devoted to finding relations between physical properties of galaxies, such as morphology, star formation rate (SFR), stellar mass, metallicity, and amount of gas, both for spatially-resolved regions and galaxies as a whole~\citep[e.g.][]{Wong13,Leroy08}, and many others use these results in analyzing observations of high-redshift galaxies~\citep[e.g.][]{Freundlich13,Walch11}.
%Advances in technology allow us to collect data from the sky. %PB - commented out
Surveys such as KINGFISH~\citep{Kennicutt11} and THINGS~\citep{Walter08} have made observations of nearby galaxies in various wavelengths and from these data we can measure physical properties such as stellar mass, star formation rate (SFR), dust mass, and gas mass~\citep[e.g.][]{Eskew12,Dale09,Calzetti07}.

% A little bit about M31 and previous studies in M31.
The Andromeda galaxy (M31), at a distance of $\sim$~0.78~Mpc, is the closest spiral galaxy to the Milky Way~\citep{McConnachie05}.
Images of this galaxy provide us with a detailed view of the inside of a spiral galaxy as seen from an external perspective.
M31 has been observed by many telescopes including the {\textit Hubble}, \Spitzer and \Herschel space telescope.
\cite{Barmby06} used data from the \Spitzer Infrared Array Camera \citep[IRAC;][]{Fazio04} to show the spatial distribution of Polycyclic Aromatic Hydrocarbons (PAHs) in the interstellar medium (ISM) of M31.
Using data from the Multiband Imaging Photometer for Spitzer (MIPS) instrument, \cite{Gordon06} studied the morphology of M31's dust.
\cite{Azimlu11} and \cite{Sanders12} catalogued and studied \hii~regions of M31.
\cite{Draine14, Mattsson14, Viaene14, Smith12} and~\cite{Fritz12} used \Herschel data to study dust in the ISM of the galaxy.
Properties of the current stars in the galaxy were studied by many groups~\citep[e.g.][and references therein]{Tamm12,Dalcanton12,Massey07}.
\cite{Rahmani16, Ford13} and \cite{Tabatabaei10} measured the spatially-resolved SFR in M31 in order to study star formation laws, and~\cite{Dim15} and \cite{Kapala15} used infrared spectroscopy to study PAHs and atomic and molecular line emission in the ISM.

Although all these studies measured some properties of M31, or answered specific scientific questions about this galaxy, we still do not have a complete picture of underlying processes in the galaxy.
What is the correlation between PAHs and SFR, dust mass, and gas mass in M31? 
Are PAH features in M31 similar or they can be divided into various groups? If so, what are the properties of each group?
Does the intensity of PAH emission depend on the underlying structure of their position? %PB: I don't understand what you mean by "underlying structure of their position"
How do they compare to properties of galaxies? %PB: what is "they"
The properties of M31 that derived in various studies and observational data of this galaxy can be used for a knowledge discovery and data mining study.
%The amount of data for M31 makes this galaxy a suitable target for a knowledge discovery and data mining study.
The Pinwheel Galaxy (M101), with distance of 6.7~Mpc~\citep{Freedman01}, is another nearby galaxy that has been well-observed and studied~\citep[e.g. ][and references therein]{Kennicutt11,Dale09, Leroy08, Gordon08}.
M101 is a large spiral galaxy with several \hii~regions and a large metallicity gradient from centre to outskirts~\citep{Kennicutt03}.
In case of dimensionality data from M101 is a suitable addition to M31 data for a data mining study. %PB: don't understand "In case of dimensionality"
Knowledge discovery and data mining methods are designed to extract hidden information from data and have been tested in many astronomical studies~\citep[e.g.][and references therein]{Ball10}.
However, this study is the first to use a data mining method on observations of nearby galaxies.

% data mining and clustering in general; when we have so many data and we want to map them
\cite{Ball10} gave an extensive review of data mining and machine learning algorithms and their usage in astronomy.
A data mining algorithm learns about data from training, which can be supervised or unsupervised.
Supervised training refers to methods that use examples of the desired output to learn about input data; these are valuable tools for classifying data with known target values.
Unsupervised methods train without any prior knowledge of output results: 
they work solely based on the underlying structure of the input data.   
The unsupervised methods are very useful tools in knowledge discovery studies, where we have limited pre-expectations for the data or when we want to make sure that we did not miss any valuable information in previous studies.

The purpose of the present work is to use M31 observations to generate new insights into nearby galaxies, with a focus on relations between PAHs and other properties of the galaxy.
There are very few studies on relations between properties of M31 with its PAH features. %generate?!
\cite{Cesarsky98} studied PAH spectra observed by ISOCAM spectro-imaging in four regions in M31 and found that PAH features in M31 differ from those in other galaxies in having weak or no $6.2 - 8.6$~$\mu$m emission with enhanced 11.2~$\mu$m emission. 
However,~\cite{Dim15} using {\it Spitzer}/Infrared Spectrograph~\citep[IRS;][]{Houck04b} observations, found that the PAH spectra of M31 have the same features as the spectra of other nearby star-forming galaxies.
Those authors re-evaluated the ISOCAM data to compare them to IRS data and found that the earlier results were likely due to incorrect background subtraction. %(PB), but the results were inconclusive. %%%%% !!!!!%%%%
Using IRAC imaging observations,~\cite{Barmby06} found good agreement between the M31 SFR derived using observed 8~$\mu$m luminosity with other 
star formation indicators such as \halpha and far infrared luminosity.
\cite{Draine14} found that the PAH abundance in M31 is almost constant up to a galactocentric radius of $\sim 20$~kpc.
With data mining techniques we address the question of whether,
compared to other galaxies, PAH features in M31 are unique as~\cite{Cesarsky98} claimed, or  are normal as ~\cite{Dim15} and \cite{Draine14} concluded.

%this project 1 M31 and its extensive data we do not have any SOM in nearby galaxies
In this project we apply the self-organizing map algorithm (SOM) to M31 data, training 1D and 2D networks.
Using networks with fewer neurons, we study the properties of the clusters and investigate relations between PAH features and other quantities in M31.
We create 2D SOMs from subsets of the data as well as all available data, which helps us to understand the effect of each input on the position of the clusters in the SOM.
We apply the 2D trained networks to the M101 data to check whether it has similar properties.
If our hypothesis is correct, we should be able to see that regions in M31 and M101 with the same positions in the SOM have the same properties.

We describe the SOM method in Section $\S$~\ref{sec: method}. %PB: I think you use either "Section" or $\S$, not both.
In Section $\S$~\ref{Sec: data_SOMN}, we present the observational data from M31 and M101 that we use in this study.
The results of the 1D SOM networks and the study of PAHs in M31 are presented in Section $\S$~\ref{Sec: 1d_cluster}.
In Section $\S$~\ref{sec: 2d_cluster}, we present the results of 2D SOM networks and their use in extracting information about other galaxies.
In Section $\S$~\ref{sec: summary}, we summarize our results and discuss potential future work in this subject.

\section{METHOD}
\label{sec: method}
\subsection{Choosing an Algorithm}

Some of the most tested methods of data mining in astronomy are artificial neural networks (ANNs)~\citep[e.g.][and references therein]{Hossein14,Hossein16}.
ANNs are designed to work in the same way that the neurons work in a human brain.
These are networks of interconnected neurons (nodes), in which all of the connections are weighted.
These networks are used to study nonlinear and complex relations between input and output data.
One of the most well-known unsupervised neural networks in astronomy is a Kohonen self-organizing map (also called self-organizing map, or SOM).
SOMs visualize complex data~\citep{Kohonen82} and show simple geometrical relationships in non-linear high dimensional data~\citep{Kohonen98}.
The result of a SOM is a 1D or 2D network of neurons, which shows the positions of clusters and their relative distance.
Since the 1990s, many studies have utilized SOMs for object classification and clustering (e.g. classifying quasars' spectra, star/galaxy classifications, gamma-ray burst clustering and light curve classification) and photometric redshift estimation~\citep[e.g.][]{Odewahn92, Hernandez94, Murtagh95, Maehoenen95,Scaringi09,Geach12,Fustes13,Meusinger16,Rahmani16b}. %%% Why I cannot add submitted in front of the high-z paper %PB: MNRAS style guide says "Private communications or papers in preparation should be listed as such in the text, but omitted from the reference list, e.g. Smith (in preparation) shows that… " -- but I'm not clear on whether this applied to submitted papers or not

The K-means algorithm, SOMs, and hierarchical clustering are the main unsupervised methods that are used in astronomical studies~\citep[e.g.][]{DAbrusco12, Aycha16}. %%add one or two more
For both K-means and SOM algorithms, the user must define the number of clusters, and the algorithms decide how to separate the data into the desired number of clusters.
In the hierarchical clustering method, the user must define dissimilarity between the groups; the algorithm combines (or divides) existing groups based on their dissimilarity and creates a hierarchical structure. 
Comparing the SOMs, K-means and hierarchical clustering methods shows that in some cases the hierarchical clustering method mis-classifies the data~\citep[][and references therein]{Mangiameli96}.
We chose the SOM method over the K-means method due to the fact that SOMs not only cluster data, but also show similarities and dissimilarities between the clusters.
Therefore, we can cluster our sample data and study the underlying structure simultaneously.

 \subsection{Self Organizing Maps}
 \label{sec: som}
 The SOM is a clustering method which reduces the dimensionality of data, while preserving topological features~\citep{Kohonen98}. 
 The results of the SOM are shown with a map of neurons, which their numbers are set by the user.
 Each neuron has a fixed position in the map and may contain one or more samples from the input data,~\boldit{V} $\in \Re^n$. % Els said the simbols should be describe?! I think it is pretty obvious! %PB: most are pretty obvious, but mention what $n$ is here
 A weight vector,~\boldit{W} $\in \Re^n$, with the same dimension as the input data, is associated with each node and will be varied during the training process.
 The process of creating an SOM happens over a series of $N$ iterations.
 In each iteration, the algorithm calculates the Euclidean distance for each node $j$ as $D_j^2= \sum_{i=0}^{i=n} (V_i - W_i)^2$, and finds a neuron with $D_{j_,{\mathrm min}}$. 
 This neuron is the winner node and is calling Best Matching Unit (BMU). 
 The weight vectors in the neighbourhood of the BMU will change according to the Kohonen learning rule (equation~\ref{equ: weight adj}). 
  \begin{equation}
            \label{equ: weight adj}
            W(t+1)=W(t)+L(t) \times R(t) \times(V(t)-W(t))
 \end{equation}
where $L(t) = L_0 e^{(-t/\tau)}$ is the learning factor, which prevents the divergence of the SOM, and $R(t)=\exp(-\frac{D_j^2}{2r^t_{BMU}})$ is the influence rate, which determines how the weight of each node will change. %PB: mention what L_0, \tau, r are
Values for the number of neurons, $L(t)$ and $R(t)$ are arbitrary. 
~\cite{Geach12} and \cite{Rahmani16b} demonstrate the algorithm of the SOM in more detail.

     In order to create self-organizing maps, we used the \textsc{matlab} neural network toolbox~\citep[NNT,][]{matlabtolbox}.
     An SOM in \textsc{nnt} can be created by the \textsc{newsom} library, which works in two phases, the ``ordering phase" and ``tuning phase" . 
     Phase one is the ``ordering phase". 
     This phase starts with maximum neighbourhood distance, and an initial high learning factor, usually 0.9, which is provided by the user. 
     The ordering phase continues for the requested number of iterations.
     At the end of the iterations, the learning factor reduces to the tuning phase learning factor and the neighbourhood distance reaches the value set by the user. 
     The second phase is the ``tuning phase".
     In this phase the neighbourhood distance is at its minimum, but the learning factor decreases very slowly.
     This minimum neighbourhood distance and slowly decreasing learning factor helps to fine tune the topology results and causes a more stable SOM. 
     The number of iterations in this tuning phase must be much greater than the number of iterations in ordering phase, to allow the tuning to happen slowly. 
     We chose the number of epochs in the tuning phase to be 3 times more than the number of epochs in the ordering phase.

     To present our results, we use \textsc{nnt}'s built-in plotting tool.
     Specifically, we combine two of the plots in this tool: a hits map, which shows the number of times each neuron has become the winner (hits), and a distance map, which shows the distance between weight vectors of those neurons.
     In the maps, the purple hexagonal shapes show the neurons. 
     The distances are shown by the grey-scale colours: the darker the colour, the larger the distance between neurons.
     Neurons with zero hits are left empty.
     In Section~\ref{sec: mock_sample} we used \textsc{newsom} to create SOMs from a mock sample to illustrate how this method works and how to interpret the results.

     One feature of the SOM method is that there is no rule or restriction on the number of clusters.
     Users must decide the size of the network based on their data set and their usage of the results.
     There has been a few attempts to find a rule for restricting the number of neurons based on the input sample \citep[e.g.][]{Vesanto05}, but none of them are certain. 
     We varied the size of SOMs from $1\times2$ to $50\times50$ in order to choose the most suitable size for the maps we generated, and found that based on the size of our sample, the best size for the 2D SOMs was $10\times10$. 
     We created our final SOMs with initial values for number of iterations in ordering phase, ordering phase learning factor, tuning phase learning factor, and tuning phase neighbourhood distance of 500, 0.9, 0.02, and 1, respectively. 
     %Also for each grid we created different SOM with different, learning factors, neighbourhood distances, and iteration numbers to find the optimize result for our sample.
     %Based on our data we created our final SOMs with following initial values: number of iteration in ordering phase = 1000; ordering phase learning factor = 0.9; tuning phase learning factor= 0.02; and tuning phase neighbourhood distance to be 1.
     %All the other parameters are default values in \textsc{ newsom} library and cannot be changed by the users.

         \begin{figure}
                \centering
                \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/mock_sample.png}
            \caption{SOM of the mock sample. The axes show the position of the neurons. Hexagonal shapes represent the neurons. The grey-scale colours show the differences between neuron weights, where white is the minimum difference and black is the maximum one.}
            \label{fig: sample}
        \end{figure}

To show how self-organizing maps work, we created a mock sample containing only a few regions.
Each sample had two properties: the amount of dust and the star formation rate, where the possible values were
either 0 or 1 for low or high SFR, and 0 or 0.5 for a low or high amount of dust. 
 We generated an SOM from the sample with a size of $10 \times 10$, using the method described in Sec.~\ref{sec: som}.
 Fig. ~\ref{fig: sample} shows the SOM of the mock sample. 
 The axes show the position of the neurons in a $10 \times 10$ network and the hexagonal shapes are the neurons.

Using this method, as expected, we are able to divide the mock sample into 4 distinct groups. Their boundaries are shown by grey colours in Fig.~\ref{fig: sample}: regions with high SFR and high dust content, regions with low SFR and high dust content, regions with high SFR and low dust content, and regions with low SFR and dust content. 
%The plot in the Fig.~\ref{fig: sample} clearly shows these divisions.%PB: commented out.
In Fig.~\ref{fig: sample}, the upper part belongs to regions with low dust content, while the lower part belongs to regions with high dust content.
The left part of the plot is where regions with low SFR belong and the right side is for high SFR regions.
Grey to black colours show the border between regions.
This network is considered to be a trained network, and can be used to cluster any new data set with similar entries.

Having two regions with exactly the same values in all their quantities with real data is extremely unlikely. 
If, in an input data set, there are two entries with similar (but not identical) values in all dimensions, one can find a network that separates these two entries in two groups.  
However, in case of multiple similar entries in a dataset, the number of neurons must be much higher than the number of entries for complete separation.
Therefore, the user learns about similarity or dissimilarity of members of the input dataset based on the ratio of the number of entries in the dataset and  the number of neurons.

@@

\section{Study sample} %%or sample study?! %PB: study sample is OK
\label{Sec: data_SOMN}

Our study includes 10 regions in M31 (Fig.~\ref{fig: regions in m31}) and 8 regions in M101 (Fig.~\ref{fig: regions in m101}). 
These specific regions were chosen for the availability of \Spitzer/IRS 5--15$\mu$m  spectroscopy covering the PAH emission bands.
Besides PAH band strengths, for each galaxy, we use spectroscopic and photometric observations as well as their derived properties, such as SFR, stellar mass, dust luminosity (L$_{\rm dust}$) and mass, metallicity, and gas mass.
Table~\ref{tab: data} shows the full list of data for both M31 and M101.
All data were divided by the area of their region (in arcsec$^2$), to remove the distance factor from the data and compare values across galaxies.
Since the spatial resolution of the observations varies from $<1$\arcsec to 60\arcsec $\times$ 90 \arcsec, any attempt to match resolution would have caused a loss of information in some of the input quantities (e.g. the spectroscopic data).
In this project we used flux per unit area, which the convolution methods conserve~\citep{Aniano12}, as the input data.
Therefore, we did not perform any resolution matching and used data at their original resolution. %PB: Need to discuss these last few sentences; not sure I understand what you're saying.

@@

\begin{figure}
  \begin{subfigure}[b]{0.5\textwidth}
        \centering
    %\centering
        \includegraphics[width=0.97\textwidth]{../image_paper3/images0.01/M31/M31.png}
        \caption{MIPS~24 $\mu$m image of M31, with positions of 10 regions studied.}
        \label{fig: regions in m31}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.5\textwidth}
        \includegraphics[width=\textwidth]{../image_paper3/images0.01/M101/M101.png}
        \caption{IRAC 3.6 $\mu$m image of M101, with positions of  8 regions studied.}
    \label{fig: regions in m101}
    \end{subfigure}
    \caption{Position of the data in M31 (up) and M101 (down).}
\end{figure}

%   \begin{figure}
%     \subfloat[MIPS 24~$\mu$m image of M31~\citep{Gordon06}, with position of 10 regions from~\cite{Dim15} \label{fig: regions in m31}]{
%       \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M31/M31.png}
%     }
%     \hfill
%     \subfloat[IRAC 3.6~$\mu$m image of M101~\citep{Dale09}, with position of 8 regions.\label{fig: regions in m101}]{
%       \includegraphics[width=0.5\textwidth]{../image_paper3/images0.01/M101/M101.png}}
%     \caption{Position of regions that the input data for SOM that obtained from there in M31 (up) and M101 (down).}
%     \label{fig:dummy}
%   \end{figure}

    \subsection{M31 observations}
     \label{Sec: data_M31_SOMN}

     \cite{Dim15} used {\it Spitzer}/IRS observations to study PAHs in 10 regions chosen to span a range of mid-infrared flux ratios in M31 (Fig.~\ref{fig: regions in m31}). 
     Fluxes and equivalent widths of PAH and atomic line features were measured using the~\textsc{pahfit idl} tool~\citep{Smith07b}.
     \cite{Dim15} also measured metallicity and radiation hardness index (RHI) for these 10 regions.
     We used the measured PAH feature fluxes, metallicity and RHI of each region as the input for self-organizing maps.

    For the photometry part of the sample, we used the \GALEX \citep{Martin05} far-ultraviolet and near-ultraviolet (FUV and NUV) channel images; \halpha~(6574.7\AA), \sii~(6730.72\AA) and \oiii~(5024.9\AA) narrow band images~\citep{Massey07}, IRAC 3.6, 4.5, 5.8 and 8.0~$\mu$m images~\citep{Barmby06}; MIPS~24 and 70~$\mu$m~images~\citep{Gordon06}; and PACS 100 and 160~$\mu$m and SPIRE 250, 350, and 500~$\mu$m~\citep{Fritz12} images.
     The units of all fluxes were converted to W~m$^{-2}$ in order to be the same as the PAH fluxes.
     $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Nieten06} and atomic gas (\hi) 21~cm emission images from~\cite{Chemin09} were added to the input data. 
     For derived values, we utilized SFR(FUV + 24$\mu$m) measured using combination of FUV and 24$\mu$m emission, stellar mass, molecular gas mass, atomic gas mass, total gas mass, and total infrared (TIR) luminosity (L$_{\mathrm TIR}$) from~\cite{Rahmani16}, and L$_{\mathrm dust}$ and dust mass from~\cite{Draine14}.

    \subsection{M101 observations}
    \label{Sec: data_M101_SOMN}

     \cite{Gordon08} measured PAH fluxes and RHI for M101 in 8 star forming \hii~regions (Fig.~\ref{fig: regions in m101}).
     Metallicities of 6 of the 8 regions were measured by~\cite{Kennicutt03} and the other two by~\cite{Gordon08}.
     We used the NED~\footnote{The NASA/IPAC Extragalactic Database (NED) is operated by the Jet Propulsion Laboratory, California Institute of Technology, under contract with the National Aeronautics and Space Administration.} website to gather imaging observations of M101, including 
      \GALEX FUV and NUV~\citep{depaz07}, IRAC 3.6 -- 8.0~$\mu$m, MIPS~24 and 70~$\mu$m~\citep{Dale09}, and PACS~100 and 160~$\mu$m and SPIRE~250, 350, and 500~$\mu$m emission from~\cite{Kennicutt11}.
     As with M31, we used $^{12}$CO (J:$1\rightarrow0$) line emission images~\citep{Helfer03} and atomic gas (\hi) 21~cm emission images from \cite{Walter08}.
     We calculated SFR(FUV + 24$\mu$m), stellar and total gas mass maps using the same methods as for M31.

       \subsection{Preparing data for data mining}

     Correlations between some of single-wavelength emission and galaxy properties are well-known.
     Emission in the 3.6$\mu$m band traces the old stellar population very well~\citep[e.g.][]{Smith07a,Leitherer99} and it can be used to calculate the stellar mass~\citep{Eskew12}.
     FUV, \halpha, and TIR emission are indicators of star forming regions.
     In this project, we used the SFR traced by the FUV emission, corrected for foreground stars using NUV emission and for dust extinction using 24~$\mu$m emission.
     Total infrared emission is calculated from a modified version of~\cite{Draine07} calibrations using using 8, 24, 70, and 160~$\mu$m emission~\citep{Boquien10}.
